---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# cloudr

<!-- badges: start -->
<!-- badges: end -->

**This is a personal project that is in development - it is not working properly**

Just for fun, I've had a go at producing word cloud type graphics in R. At the moment, it's slow and clunky. Personally I don't believe that word clouds are a particularly useful or insightful way to visualise text analysis, but I do think they can look rather pretty and be good fun to make.

I'm not really interested in developing code to extract words and their respective weights from a body of text. Here I am just interested in how to place the words (scaled to their weighting) on the page in the form of a word cloud. As such, the code im developing here needs to be supplied with a vector of words and a vector of their weights from which a word cloud will be generated.

## Add package to search path
```{r}
library(cloudr)
```

## Default data set
`cloudr` has a raw data set `obama` - a dataframe of words and their weights from Obama's 2016 state of the union speech downloaded from https://help.xlstat.com/customer/en/portal/articles/2918639-word-cloud-tutorial-in-excel-?b_id=9283
```{r}
obama[1:10, ]
```

## Create word cloud
```{r fig.width=8, fig.height=6, fig.align='center', results='hide'}
wc(obama$word[1:100], obama$count[1:100], 
   seed=4,
   lower_cex = 0.5, 
   upper_cex = 6,
   lo_col = "grey",
   markup = FALSE)

wc(obama$word[1:100], obama$count[1:100], 
   seed=4,
   lower_cex = 0.5, 
   upper_cex = 6,
   hi_col = "orange",
   lo_col = "red",
   markup = TRUE)
```
