---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width=10, 
  fig.height=8,
  out.width = "100%",
  fig.align='center')
```
# cloudr - bitmap (using fontr)

<!-- badges: start -->
<!-- badges: end -->

## **This is a personal project and a work in progress. It is not working properly**

I've had a go at producing word cloud type graphics in R in order to learn and devlop my coding skill. Personally I don't believe that word clouds are a particularly useful or insightful way to visualise text analysis, but I do think they can look rather pretty and be good fun to make.

This 'bitmap' version of `cloudr` uses Yixuan's rather marvellous [fontr](https://github.com/yixuan/fontr) package in order to return bitmaps of the character glyphs. This allows for much faster collision detection of matrices.

## Add package to search path
```{r}
library(cloudr)
```

## Default data set
`cloudr` has a raw data set `obama` - a dataframe of words and their weights from Obama's 2016 state of the union speech downloaded from https://help.xlstat.com/customer/en/portal/articles/2918639-word-cloud-tutorial-in-excel-?b_id=9283
```{r}
obama[1:10, ]
```

## Create word clouds

```{r results='hide'}
bmwc(cloudr::obama[1:200,], seed = 42)
```

```{r results='hide'}
bmwc(cloudr::obama[1:200,], angle_range = c(-10,10), seed = 42)
```


### Change font
```{r results='hide'}
sysfonts::font_add(family = "old_eng", "C:/Windows/Fonts/OLDENGL.TTF")
bmwc(obama[1:200,], font_family = "old_eng", seed=42)
bmwc(obama[1:200,], font_family = "old_eng", seed=42, angle_range = c(-25,25))
```
